Placeholder

### 2021-02-22 Paper_Histograms.Rmd
Added space between July - September in retro sign up chart

dat.retro_july_sep_sign_up <- dat.retro_july_sep_sign_up %>% 
  group_by(Sample_plot) %>% 
  mutate("July-September" = 
           July + August + September) %>% 
  select(Sample_plot, "July-September")

@@

dat.retro_sign_up$month <- factor(dat.retro_sign_up$month,
                                  levels = c("April", "May", "June", "July-September"))

>>>>

dat.retro_july_sep_sign_up <- dat.retro_july_sep_sign_up %>% 
  group_by(Sample_plot) %>% 
  mutate("July - September" = 
           July + August + September) %>% 
  select(Sample_plot, "July - September")

@@

dat.retro_sign_up$month <- factor(dat.retro_sign_up$month,
                                  levels = c("April", "May", "June", "July - September"))
